#Getting and Cleaning Data peer assignment 1

1.Merges the training and the test sets to create one data set.

```{r}
#load data
test<-read.table(file = "UCI HAR Dataset/test/X_test.txt",header = FALSE)
train<-read.table(file = "UCI HAR Dataset/train/X_train.txt", header = FALSE)
#merge data
a<-rbind(train, test)
```

2.Extracts only the measurements on the mean and standard deviation for each measurement. 

```{r}
#load data
features <- read.table(file = "UCI HAR Dataset/features.txt", header = FALSE)
b<-features[,2]
#extract data
c<- grep("mean\\(\\)|std\\(\\)", b)
a<-a[,c]
colnames(a) <- gsub('mean\\()', "mean", b[c])
colnames(a) <- gsub('std\\()', "std", colnames(a))
```

3.Uses descriptive activity names to name the activities in the data set

```{r}
#load activity names
activity1<-read.table(file = "UCI HAR Dataset/activity_labels.txt",head=FALSE)
ytest <- read.table(file = "UCI HAR Dataset/test/y_test.txt", header = FALSE)
ytrain<-read.table(file = "UCI HAR Dataset/train/y_train.txt", header = FALSE)
y<-rbind(ytrain, ytest)
#use activity names to name the activities in the data set
activity<- activity1[y[, 1], 2]
```

4.Appropriately labels the data set with descriptive activity names 

```{r}
subjectte <-read.table(file = "UCI HAR Dataset/test/subject_test.txt", header = FALSE)
subjecttr<-read.table(file = "UCI HAR Dataset/train/subject_train.txt", header = FALSE)
subject = rbind(subjecttr, subjectte)
colnames(subject)<-"subject"
a<-cbind(activity,subject,a)
write.table(a, "tidy_data1.txt")#output the tidy data set
```

5.Creates a second, independent tidy data set with the average of each variable for each activity and each subject. 

```{r}
#contruct a new dataframe
tidy<-matrix(NA,length(unique(a[,1]))*length(unique(a[,2])),dim(a)[2])
tidy<-as.data.frame(tidy)
k=1
for (i in 1:length(unique(a[,1])))
  {d<-a[a[,1]==unique(a[,1])[i],2:dim(a)[2]]
   for ( j in 1:length(unique(a[,2])))
   {
     e<-d[d[,1]==unique(a[,2])[j],2:dim(d)[2]]
     tidy[k,1]<-as.character(unique(a[,1])[i])
     tidy[k,2]<-unique(a[,2])[j]
     tidy[k,3:dim(a)[2]]<-apply(e,2,mean)#mean of every column
     k<-k+1
   }
   }
colnames(tidy)<-colnames(a)
write.table(tidy, "tidy_data2.txt")#output the tidy data set
```